---
title: "Modeling and prediction for movies"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(GGally)
```

### Load data

 

```{r load-data}
 setwd("C:\\DataScinceTrack\\DUKE\\DUKE-STAT-COURSES\\Rgression_project")
load("movies.Rdata")
 
```



* * *

## Part 1: Data

*  Rrandomly sampled movies released before 2016.
        -we cannot perform    causation since it can only be inferred from a randomized experiment.(and no expermint here).
        - associations. cant be infered since observational studies are generally only used to show associations.
        - only correlations can be infered and since the sampling is random the results are generalisable to the bigger population
* * *

## Part 2: Research question

Response variable:
explantory variables :

does  best_pic_nom ,best_pic_win best_actor_win,best_actress_win, best_dir_win, top200_box
affected (have influence on) audience_score

* * *

## Part 3: Exploratory data analysis
```{r}
#Exploring Data
nrow(movies)
ncol(movies)
str(movies)

head(movies)
# head(movies[, c(1:15, 10)])
# 
# head(movies[, c(15:25, 10)])
# 
# head(movies[, c(25:32, 10)])


#unique(movies$actor1)

# unique(movies$audience_rating)
# unique(movies$critics_rating)
# unique(movies$mpaa_rating)
# unique(movies$studio)
# unique(movies$title_type)

summary(movies$audience_score)
summary(movies$critics_score)

# group movies by type 
movies_type_group  <- group_by(movies, title_type ) %>%
        summarize(movies = mean(audience_score))  

movies_type_group

movies_arranged  <-  arrange(movies, desc( audience_score))


# top 10 score movies
head(movies_arranged[ ,1], 10)

#last 10
tail(movies_arranged[ ,1], 10)
 
 
#EXPLORE DATA USING PLOTS
# replace character values from col 19 to 24 with numeric values yes=1 and no =0



#from summary we  can see that highest and min score for audiances and critics

 
movies[19:24]<-ifelse(movies[19:24] =='yes', 1,0)
ggpairs(movies, columns = 19:24)

par(mfrow = c(1, 3), mar = c(4, 4, 2, 1))
boxplot( movies[movies$title_type=='Documentary', ]$audience_score , xlab= " Documentary" ,col= "yellow")
boxplot( movies[movies$title_type=='Feature Film', ]$audience_score , xlab= " Feature Film" ,col= "red" )
boxplot( movies[movies$title_type=='TV Movie', ]$audience_score , xlab= " TV Movie" ,col= "green" )

#audiance score scatter plot
plot(movies$audience_score)

Palette1 <- c('red','green','violet','black')
ggplot( data=movies, aes(y=audience_score,x= title )) +
        geom_point(aes(colour =title_type))+
  scale_colour_manual(values=Palette1 )
```





* * *

## Part 4: Modeling

 

Model the relation between audience_score as respnose variable and   columns   19:24
best_pic_nom ,best_pic_win best_actor_win,best_actress_win, best_dir_win, top200_box
```{r}
movies[1:5,19:24]
movies[19:24]<-ifelse(movies[19:24] =='yes', 1,0)
ggpairs(movies, columns = 19:24)
 
#  parametersnot corolated strongly
# backword modeling method 0 full mpdel


m_full <- lm(audience_score ~ best_pic_nom + best_pic_win + best_actor_win + best_actress_win + best_dir_win + top200_box , data = movies)
summary(m_full)
summary(m_full)$adj.r.squared


qqnorm(m_full$residuals)
qqline(m_full$residuals)
 
```
#remove heighest p-value >> best_pic_winyes 
```{r}
ml <- lm(audience_score ~ best_pic_nom +   best_actor_win + best_actress_win + best_dir_win + top200_box , data = movies)
summary(ml)
summary(ml)$adj.r.squared
```

#remove best_actress_winyes

```{r}
ml <- lm(audience_score ~ best_pic_nom +   best_actor_win + best_dir_win + top200_box , data = movies)
summary(ml)
summary(ml)$adj.r.squared
```

best_actor_winye
```{r}
ml <- lm(audience_score ~ best_pic_nom +    best_dir_win + top200_box , data = movies)
summary(ml)
summary(ml)$adj.r.squared

qqnorm(ml$residuals)
qqline(ml$residuals)
```

#remove best_dir_winyes  removing it will make results worse for that the model will be the one above 
```{r}
ml <- lm(audience_score ~ best_pic_nom +    best_dir_win  , data = movies)
summary(ml)
summary(ml)$adj.r.squared


#bac to the previous model
ml <- lm(audience_score ~ best_pic_nom +    best_dir_win + top200_box , data = movies)
summary(ml)
summary(ml)$adj.r.squared

```


* * *

## Part 5: Prediction
predict movie score where  best_pic_nom =0 nd  best_dir_win=0 and top200_box=0
also preict when  best_pic_nom =1 nd  best_dir_win=1 and top200_box=1
and best_pic_nom =1 nd  best_dir_win=0 and top200_box=1
```{r}
newscore <- data.frame(best_pic_nom = 0, best_dir_win = 0, top200_box=0)
predict(ml, newscore)
predict(ml, newscore, interval = "prediction", level = 0.95)

#  best_pic_nom =1 and  best_dir_win=1 and top200_box=1
 newscore <- data.frame(best_pic_nom = 1, best_dir_win =1, top200_box=1)
predict(ml, newscore)
# best_pic_nom =1 nd  best_dir_win=0 and top200_box=1

 newscore <- data.frame(best_pic_nom = 1 ,best_dir_win =0, top200_box=1)
predict(ml, newscore)
```

* * *

## Part 6: Conclusion

 I should use other vaiables and try better parameters since the model parameters shrinks to almost linear one.